\part{Take Care of Yourself}
\label{takecareofyourself}

\chapter{Health and Wellness}
\label{healthandwellness}

\begin{itemize}
\item Do I actively try to keep myself healthy?

\begin{itemize}
\item If I have a physical health issue, do I make my own doctor's appointments, unprompted?

\item Do I schedule my own regular visits to the dentist, unprompted?

\item Do I eat well, unprompted?

\item Do I exercise regularly, unprompted?

\end{itemize}

\item Do I practice good personal hygiene?

\item Do I regularly wash my clothes myself?

\end{itemize}

\chapter{Home Care}
\label{homecare}

\begin{itemize}
\item Do I keep my home clean?

\begin{itemize}
\item What are my standards for home cleanliness?

\item Am I proud of your home's level of cleanliness?

\item Am I getting \emph{everything}? Including the baseboards and the dust on tops of the window frames?

\end{itemize}

\item Do I keep my home minimally cluttered and welcoming?

\item Do I practice good personal hygiene?

\item Do I have good laundry habits?

\begin{itemize}
\item Regularly washing clothes

\item Regularly washing and changing sheets (and comforter\slash duvet cover\slash pillowcases)

\item Regularly washing towels

\end{itemize}

\end{itemize}

\part{Partnered Life}
\label{partneredlife}

\begin{itemize}
\item Am I checking in with my partner to see if they had a rough day?

\item If so, am I stepping up to make their life easier in other ways (cooking, cleaning, etc.)?

\item Am I open and clear about my wants, and not forcing my partner to guess\slash drag it out of me?

\item Am I contributing constructively to planning of meals, events, trips, etc?

\item Am I actively trying to make my presence feel safe for my partner?

\item Do I try to do nice things for my partner without being asked (flowers, treats, etc.)?

\item Do I take care of my own administrative life (paperwork, bills) without needing to be repeatedly reminded?

\item Am I supportive of my partner's decisions, big and small?

\item Am I respectful and validating of my partner's emotions?

\item Am I vocally grateful when my partner goes out of their way to do something nice for me?

\item Am I nice to my partner's family [if that's a thing they want]?

\end{itemize}

\part{Friend Groups}
\label{friendgroups}

\begin{itemize}
\item Do I work to coordinate peoples' schedules so that we can have a nice picnic\slash party\slash board game night\slash etc.?

\item When planning an event, am I conscious of possible interpersonal conflicts?

\item When planning an event, do I take into account different peoples' preferences for food, beverages, music, etc., so that no one feels excluded?

\item Do I actually have everything prepared in advance for an event I'm hosting, or at least clearly and fairly delegated?

\item If there is an imbalance of emotional or physical labor occurring, am I willing to risk social awkwardness to improve the lot of those negatively affected?

\end{itemize}

\part{Third Party Relationships (Familial \& Otherwise)}
\label{thirdpartyrelationshipsfamilialotherwise}

\begin{itemize}
\item Do I remember to make phone calls and visits to people I care about and want to have relationships with?

\item Do I remember to send cards to people I care about?

\item Do I send thank you notes to people to acknowledge their emotional labor for me?

\item Am I actively sensitive to and supportive of people who are experiencing a difficult time (death of spouse\slash child\slash pet, etc.)?

\end{itemize}
